\bf Eye Fitting Straight Lines in the Modern Era

### 2022-10-14 Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd
final revisions submtted :) yay

authors: 
- name: Emily A. Robinson 1
  # thanks: The authors gratefully acknowledge ...
  affiliation: Department of Statistics, University of Nebraska - Lincoln

@@

# Plot Predictions
eyefitting.lmer.plot <- eyefitting.preds.lmer %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = asymp.LCL.ols, ymax = asymp.UCL.ols, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.ols, color = "OLS")) +
  geom_ribbon(aes(ymin = asymp.LCL.pca, ymax = asymp.UCL.pca, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.pca, color = "PA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 4, labeller = label_both) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PA")) +
  scale_fill_manual("LMER fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PA"))

@@

```{r eyefitting-gamm-residualplots, fig.height = 3, fig.width = 9, out.width = "100%", fig.cap = "Estimated trend line of the residuals between the participant drawn points and fitted values for both the OLS (blue) regression line and PA (orange) regression line determined by smoothing splines fit by a generalized additive mixed model. Estimated residual trends with 95\\% confidence bands are overlaid on the observed individual participant residuals."}
eyefitting.grid.gamm <- read_csv("analysis/youdrawit-eyefitting-gammpred-data.csv")
# Plot Predictions
eyefitting.gamm.plot <- eyefitting.grid.gamm %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.2) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.2) +
  geom_ribbon(aes(ymin = ols.lower, ymax = ols.upper, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = ols.pred, color = "OLS")) +
  geom_ribbon(aes(ymin = pca.lower, ymax = pca.upper, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = pca.pred, color = "PA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 4, labeller = label_both) +
  # facet_wrap(`Parameter Choice`, ncol = 4, labeller = label_both) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PA")) +
  scale_fill_manual("GAMM fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PA")) 
eyefitting.gamm.plot
```

@@

<!-- + **Study Applet:** The shiny app used to conduct the study can be accessed at  [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). -->
<!-- + **RShiny Applet Code:** The code used to create the RShiny Applet for data collection can be found at [https://github.com/earobinson95/you-draw-it-validation-applet(https://github.com/earobinson95/you-draw-it-validation-applet). -->
+ **Participant Data:** De-identified participant data collected in the study and used for analyses (eyefitting-model-data.csv).
<!-- `eyefitting-model-data.csv` or may be downloaded from GitHub at  [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data).  -->
+ **Data Analysis Code:** The code used to replicate the analysis in this paper (you-draw-it-eyefitting-analysis.Rmd).
<!-- or found at [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/analysis/you-draw-it-eyefitting-analysis.Rmd](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/supplementary-materials/you-draw-it-eyefitting-analysis.Rmd). -->
+ **readme:** File containing detailed descriptions of the supplementary material (README.html).

>>>>

authors: 
- name: Emily A. Robinson 1
  thanks: The authors report there are no competing interests to declare.
  affiliation: Department of Statistics, University of Nebraska - Lincoln

@@

# Plot Predictions
eyefitting.lmer.plot <- eyefitting.preds.lmer %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.1) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), 
            aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.1) +
  geom_ribbon(aes(ymin = asymp.LCL.ols, ymax = asymp.UCL.ols, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.ols, color = "OLS")) +
  geom_ribbon(aes(ymin = asymp.LCL.pca, ymax = asymp.UCL.pca, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = emmean.pca, color = "PA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 4, labeller = label_both) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PA")) +
  scale_fill_manual("LMER fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PA"))

@@

```{r eyefitting-gamm-residualplots, fig.height = 3, fig.width = 9, out.width = "100%", fig.cap = "Estimated trend line of the residuals between the participant drawn points and fitted values for both the OLS (blue) regression line and PA (orange) regression line determined by smoothing splines fit by a generalized additive mixed model. Estimated residual trends with 95\\% confidence bands are overlaid on the observed individual participant residuals."}
eyefitting.grid.gamm <- read_csv("analysis/youdrawit-eyefitting-gammpred-data.csv")
# Plot Predictions
eyefitting.gamm.plot <- eyefitting.grid.gamm %>%
  filter((parm_id %in% c("F", "N", "S") | (x <= 16 & x >= 4))) %>%
  mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>%
  dplyr::rename(`Parameter Choice` = parm_id) %>%
  ggplot(aes(x = x)) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_ols_drawn, group = plot_id, color = "OLS"), alpha = 0.1) +
  geom_line(data = eyefitting_model_data %>% mutate(parm_id = factor(parm_id, levels = c("S", "F", "V", "N"))) %>% dplyr::rename(`Parameter Choice` = parm_id), aes(x = x, y = residual_pca_drawn, group = plot_id, color = "PA"), alpha = 0.1) +
  geom_ribbon(aes(ymin = ols.lower, ymax = ols.upper, fill = "OLS"), color = NA, alpha = 0.4) +
  geom_line(aes(y = ols.pred, color = "OLS")) +
  geom_ribbon(aes(ymin = pca.lower, ymax = pca.upper, fill = "PA"), color = NA, alpha = 0.4) +
  geom_line(aes(y = pca.pred, color = "PA")) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~`Parameter Choice`, ncol = 4, labeller = label_both) +
  # facet_wrap(`Parameter Choice`, ncol = 4, labeller = label_both) +
  theme_bw(base_size = 14) +
  theme(aspect.ratio = 1,
        legend.position = "right",
        plot.title   = element_text(size = 12, hjust = 0),
        axis.text    = element_text(size = 12),
        axis.title   = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text  = element_text(size = 12),
        # strip.text = element_text(size = 5, margin = margin(0.05,0,0.05,0, "cm")),
        # strip.background = element_rect(size = 0.5),
        legend.key.size = unit(1, "line")
        ) +
  scale_y_continuous("Residual") +
  scale_color_manual("Individual participant \nresiduals", values = c("steelblue", "orange"), labels = c("OLS", "PA")) +
  scale_fill_manual("GAMM fitted trend", values = c("steelblue", "orange"), labels = c("OLS", "PA")) 
eyefitting.gamm.plot
```

@@

<!-- + **Study Applet:** The shiny app used to conduct the study can be accessed at  [https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/](https://emily-robinson.shinyapps.io/you-draw-it-validation-applet/). -->
<!-- + **RShiny Applet Code:** The code used to create the RShiny Applet for data collection can be found at [https://github.com/earobinson95/you-draw-it-validation-applet(https://github.com/earobinson95/you-draw-it-validation-applet). -->
+ **Participant Data:** De-identified participant data collected in the study and used for analyses (eyefitting-model-data.csv).
<!-- `eyefitting-model-data.csv` or may be downloaded from GitHub at  [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/data).  -->
+ **Data Analysis Code:** The code used to replicate the analysis in this paper (you-draw-it-eyefitting-analysis.Rmd).
<!-- or found at [https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/analysis/you-draw-it-eyefitting-analysis.Rmd](https://github.com/earobinson95/Eye-Fitting-Straight-Lines-in-the-Modern-Era/tree/main/supplementary-materials/you-draw-it-eyefitting-analysis.Rmd). -->
+ **README:** File containing detailed descriptions of the supplementary material (README.html).

### 2022-10-14 manuscript-revisions/final-submission-cover-letter.qmd
final revisions submtted :) yay

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.pdf`
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.Rmd`
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex`
+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.pdf`
+ `bibliography.bib`
+ `agsm.bst`
+ `images/ydi-stimuli.png`
+ `figure-latex/eyefitting-example-plot-1.pdf`
+ `figure-latex/eyefitting-gamm-residualplots-1.pdf`
+ `figure-latex/eyefitting-lmer-residualplots-1.pdf`
+ `figure-latex/eyefitting-simplot-1.pdf`
+ `figure-latex/ols-vs-pca-example-1.pdf`

@@

+ `README.html` 
+ `eyefitting-model-data.csv`
+ `you-draw-it-eyefitting-analysis.Rmd`

>>>>

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.pdf` Final pdf version of manuscript.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex` Final latex file outputted from the rmarkdown template.

+ `bibliography.bib` File containing references in bibtex format.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era.bbl` File containing the references.

+ `images/ydi-stimuli.png` Image for Figure 1 in the manuscript.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era_files/figure-latex/`

    `eyefitting-simplot-1.pdf` Image for Figure 2 in the manuscript; originally created using R ggplot2 code within the rmarkdown file.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era_files/figure-latex/`

    `ols-vs-pca-example-1.pdf` Image for Figure 3 in the manuscript; originally created using R ggplot2 code within the rmarkdown file.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era_files/figure-latex/`

    `eyefitting-example-plot-1.pdf` Image for Figure 4 in the manuscript; originally created using R ggplot2 code within the rmarkdown file.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era_files/figure-latex/`

    `eyefitting-lmer-residualplots-1.pdf` Image for Figure 5 in the manuscript; originally created using R ggplot2 code within the rmarkdown file. This image is to be printed in color; we have emailed co-editors Galin Jones and Faming Liang about the appeal process for color costs.

+ `Eye-Fitting-Straight-Lines-in-the-Modern-Era_files/figure-latex/`

    `eyefitting-gamm-residualplots-1.pdf` Image for Figure 6 in the manuscript; originally created using R ggplot2 code within the rmarkdown file. This image is to be printed in color; we have emailed co-editors Galin Jones and Faming Liang about the appeal process for color costs.

@@

+ `README.html` File containing detailed descriptions of the supplementary material.

+ `eyefitting-model-data.csv` De-identified participant data collected in the study and used for analyses.

+ `you-draw-it-eyefitting-analysis.Rmd` The .Rmd code file used to replicate the analysis in this paper.

### 2022-10-14 manuscript/Eye-Fitting-Straight-Lines-in-the-Modern-Era.tex
final revisions submtted :) yay

  \author{
        Emily A. Robinson 1 \\
    Department of Statistics, University of Nebraska - Lincoln\\
     and \\     Reka Howard 2 \\
    Department of Statistics, University of Nebraska - Lincoln\\
     and \\     Susan VanderPlas 3 \\
    Department of Statistics, University of Nebraska - Lincoln\\
      }
  \maketitle
} \fi

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses (eyefitting-model-data.csv).
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper (you-draw-it-eyefitting-analysis.Rmd).
\item
  \textbf{readme:} File containing detailed descriptions of the
  supplementary material (README.html).
\end{itemize}

>>>>

  \author{
        Emily A. Robinson 1 \thanks{The authors report there are no
competing interests to declare.} \\
    Department of Statistics, University of Nebraska - Lincoln\\
     and \\     Reka Howard 2 \\
    Department of Statistics, University of Nebraska - Lincoln\\
     and \\     Susan VanderPlas 3 \\
    Department of Statistics, University of Nebraska - Lincoln\\
      }
  \maketitle
} \fi

@@

\begin{itemize}
\tightlist
\item
  \textbf{Participant Data:} De-identified participant data collected in
  the study and used for analyses (eyefitting-model-data.csv).
\item
  \textbf{Data Analysis Code:} The code used to replicate the analysis
  in this paper (you-draw-it-eyefitting-analysis.Rmd).
\item
  \textbf{README:} File containing detailed descriptions of the
  supplementary material (README.html).
\end{itemize}
